The KMOS Deep Survey (KDS): dynamical measurements of $z\sim3.5$ main sequence galaxies\thanks{Based on observations obtained at the Very Large Telescope of the European Southern Observatory. Programme IDs: }

### 2017-05-19 paper.tex
highlighted and ready for re-submission

% Abstract of the paper
\begin{abstract}
We present dynamical measurements from the KMOS ({\it K}-band Multi-Object Spectrograph) Deep Survey (KDS), which is comprised of 77 typical star-forming galaxies at $z\simeq3.5$ in the mass range $9.0 < log(M_{\star}/M_{\odot}) < 10.5$.
These measurements constrain the internal dynamics, the intrinsic velocity dispersions ($\sigma_{int}$) and rotation velocities ($V_{C}$) of galaxies in the high-redshift Universe.
The mean velocity dispersion of the galaxies in our sample is $\sigma_{int} = 70.8^{+3.3}_{-3.1} km\,s^{-1}$, revealing that the increasing average $\sigma_{int}$ with increasing redshift, reported for $z\lesssim2$, continues out to $z\simeq3.5$.
Only $34 \pm 8\%$ of our galaxies are rotation-dominated ($V_{C}/\sigma_{int}$ > 1), with the sample average $V_{C}/\sigma_{int}$ value much smaller than at lower redshift.
After carefully selecting comparable star-forming samples at multiple epochs, we find that the rotation-dominated fraction evolves with redshift with a $z^{-0.2}$ dependence. 
The rotation-dominated KDS galaxies show no clear offset from the local rotation velocity-stellar mass (i.e. $V_{C}-M_{\star}$) relation, although a smaller fraction of the galaxies are on the relation due to the increase in the dispersion-dominated fraction.
These observations are consistent with a simple equilibrium model picture, in which random motions are boosted in high-redshift galaxies by a combination of the increasing gas fractions, accretion efficiency, specific star-formation rate and stellar feedback and which may provide significant pressure support against gravity on the galactic disk scale.
\end{abstract}

@@

\noindent
In this paper we present new results from the KMOS Deep Survey (KDS), which is a guaranteed time programme focusing on the spatially-resolved properties of main-sequence SFGs at $z\simeq3.5$, a time when the universe was building to peak activity.
With this survey, we aim to complement existent studies by providing deep IFS data for the largest number of galaxies at this redshift.
By making use of KMOS (with integration times of 7.5-9 hours), we have been able to study [O~{\sc III}]$\lambda$5007 emission in 77 galaxies spanning the mass range $9.0 < log(M_{\star}/M_{\odot}) < 10.5$, roughly tripling the number of galaxies observed via IFS at $z > 3$.
In order to interpret the evolution of the physical properties of typical star-forming galaxies we have carefully constructed a set of comparison samples spanning $0 < z < 3$.
These samples use integral-field spectroscopy to track the ionised gas emission in star-forming galaxies and follow consistent kinematic parameter extraction methods.  
By doing this we seek to minimise the impact of systematic differences introduced by differing approaches to defining and extracting kinematic parameters.

@@

\noindent
The structure of the paper is as follows.
In \cref{sec:Survey_and_data} we present the survey description, sample selection, observation strategy and data reduction, leading to stacked datacubes for each of the KDS galaxies.
In \cref{sec:analysis} we describe the derivation of morphological and kinematic properties for our galaxies, explaining the kinematic modelling approach and the beam-smearing corrections which lead to intrinsic measurements of the rotation velocities, $V_{C}$, and velocity dispersions $\sigma_{int}$ for each of the galaxies classified as morphologically isolated and spatially-resolved in the [O~{\sc III}]$\lambda$5007 emission line.
\cref{sec:results} presents an analysis of these derived kinematic parameters, comparing with lower redshift work where possible and drawing conclusions about the evolutionary trends and possible underlying physical mechanisms.
We discuss these results in \cref{sec:discussion} and present our conclusions in \cref{sec:conclusion}.
Throughout this work we assume a flat $\Lambda$CDM cosmology with (h, $\Omega_{m}$, $\Omega_{\Lambda}$) = (0.7, 0.3, 0.7).

\section{SURVEY DESCRIPTION, SAMPLE SELECTION AND OBSERVATIONS}\label{sec:Survey_and_data}
\subsection{The KDS survey description and sample selection}\label{subsec:survey_intro}
The KDS is a KMOS study of the gas kinematics and metallicity in 77 SFGs with a median redshift of $z\simeq3.5$, probing a representative section of the galaxy main-sequence.
The addition of these data approximately triples the number of galaxies observed via IFS at this redshift \citep{Cresci2010,Lemoine-Busserolle2010,Gnerucci2011}, and will allow for a statistically-significant investigation of the dynamics and metal content of SFGs during a crucial period of galaxy evolution. 
The key science goals of the KDS are to investigate the resolved kinematic properties of high-redshift galaxies in the peak epoch of galaxy formation (particularly the fraction of rotating disks and the degree of disk turbulence) and also to study the spatial distribution of metals within these galaxies in the context of their observed dynamics.
We seek to probe both a `field' environment in which the density of galaxies is typical for this redshift and a `cluster' environment containing a known galaxy over-density, in order to gauge the role of environment in determining the kinematics and metallicities of SFGs during this early stage in their formation history.
To achieve this we require very deep exposure times in excess of 7 hours on source to reach the signal-to-noise required to detect line emission in the outskirts of the galaxies where the rotation curves begin to flatten, and to achieve adequate signal-to-noise across several ionised emission lines within individual spatial pixels (spaxels).
Consequently, the KDS is one of the deepest spectroscopic datasets available at this redshift.

@@

 \hline
Pointing & RA & DEC & N$_{obs}$ & N$_{Det}$ & $\%$ Det. & N$_{Res}$ & $\%$ Res & N$_{Merg}$ & $\%$ Merg$^{*}$ & Band$^{a}$ & Exp (ks) & PSF ($^{\prime\prime}$)$^{b}$  \\
 \hline
 \scriptsize{\bf GOODS-S-P1(field)} & 03:32:25.910 & $-$27:51:58.710 & 20 & 16 & 80 & 13 & 65 & 2 & 17 & {\it K} & 32.4 & 0.50 \\
\scriptsize{\bf GOODS-S-P2(field)} & 03:32:32.217 & $-$27:43:08.000 & 17 & 14 & 82 & 13 & 76 & 2 & 18 & {\it K} & 31.8 & 0.52 \\
\scriptsize{\bf SSA22-P1(cluster)} & 22:17:11.867 & $+$00:15:44.700 & 21 & 15 & 71 & 9 & 46 & 8 & 89 & {\it HK} & 38.1 & 0.62 \\
\scriptsize{\bf SSA22-P2(field)} & 22:17:35.120 & $+$00:09:30.500 & 19 & 17 & 89 & 12 & 63 & 2 & 18 & {\it HK} & 27.8 & 0.57 \\

@@

\noindent
We prepared each pointing using the KARMA tool \citep{Wegner2008}, taking care to allocate at least one IFU to observations of a `control' star closeby on the sky to allow for precise monitoring of the evolution of seeing conditions and the shift of the telescope away from the prescribed dither pattern (see \cref{subsubsec:datareduction}).
For the four pointings described above and summarised in Table \ref{tab:pointings}, we adopted the standard object-sky-object (OSO) nod-to-sky observation pattern, with 300s exposures and alternating $0.2^{\prime\prime}$/$0.1^{\prime\prime}$ dither pattern for increased spatial sampling around each of the target galaxies.
This procedure allowed for datacube reconstruction with 0.1$^{\prime\prime}$ size spaxels as described in \cref{subsubsec:datareduction}. \\

\noindent
The observations were carried out during ESO observing periods P92-P96 using Guaranteed Time Observations (Programme IDs: 092.A-0399(A), 093.A-0122(A,B), 094.A-0214(A,B),095.A-0680(A,B),096.A-0315(A,B,C)) with excellent seeing conditions.
In GOODS-S-P1 and GOODS-S-P2 the median {\it K}-band seeing was $\simeq0.5^{\prime\prime}$ and for the SSA22-cluster and SSA22-field pointings the {\it K}-band seeing ranged between $\simeq0.55-0.65^{\prime\prime}$.
We observed 17-21 $z\simeq3.5$ targets in each field (see Table \ref{tab:pointings}), with these numbers less than the available 24 arms for each pointing due to the combination of three broken pickoff arms during the P92/93 observing semesters and our requirement to observe at least one control star throughout an Observing Block (OB). \\

\noindent
This paper is concerned with the spatially-resolved kinematics of the KDS galaxies.
Consequently, we now focus exclusively on the spatially-resolved [O~{\sc III}]$\lambda$5007 measurements in the {\it K}-band spectral window. 
The details of the {\it H}-band data reduction and corresponding metallicity analyses will be described in a future study.

@@

The SPARK recipes were used to create dark frames and to flatfield, illumination correct and wavelength calibrate the raw data.
An additional step, which is not part of the standard reduction process, was carried out at this stage, which is to address readout channel bias.
Differences in the readout process across each 64-pixel wide channel on the detector image lead to varying flux baselines in these channels.
We corrected back to a uniform flux baseline across the detector image for each object exposure by identifying pixels which are not illuminated in every readout channel and subtracting their median value from the rest of the pixels in the channel.

\noindent
Standard star observations were carried out on the same night as the science observations and were processed in an identical manner to the science data.
Following this pre-processing, each of the object exposures was reconstructed independently, using the closest sky exposure for subtraction, to give more control over the construction of the final stacks for each target galaxy.
Each 300s exposure was reconstructed into a datacube with interpolated $0.1\times0.1^{\prime\prime}$ spaxel size, facilitated by the subpixel dither pattern discussed in \cref{subsubsec:Obs} which boosts the effective pixel scale of the observations. \\

\noindent
Sky subtraction was enhanced using the SKYTWEAK option within SPARK \citep{Davies2007}, which counters the varying amplitude of OH lines between exposures by scaling `families' of OH lines independently to match the data.
Wavelength miscalibration between exposures due to spectral flexure of the instrument is also accounted for by applying spectral shifts to the OH families during the procedure, and in general the use of the SKYTWEAK option in the {\it K}-band greatly reduces the sky-line residuals. 
We monitored the evolution of the atmospheric PSF and the position of the control stars over the OBs, to allow us to reject raw frames where the averaged {\it K}-band seeing rose above $0.8^{\prime\prime}$ and to measure the spatial shifts required for the final stack more precisely.
The PSF was determined by fitting the collapsed {\it K}-band image of the stacked control stars in each pointing with an elliptical gaussian, with the values reported in Table \ref{tab:pointings}.
The telescope tends to drift from its acquired position over the course of an OB and the difference between the dither pattern shifts and the measured position of the control stars provides the value by which each exposure must be shifted to create the stack. \\

\noindent
We stacked all 300s exposures for each galaxy which pass the seeing criteria using 3-sigma clipping, leaving us with a flux and wavelength-calibrated datacube for every object in the KDS sample.
We have found that the thermal background is often under-subtracted across the spatial extent of the cube following a first pass through the pipeline, leading to excess flux towards the long wavelength end of the {\it K}-band.
To account for this, a polynomial function is fit, using the python package {\scriptsize LMFIT} \citep{Newville2014}, which makes use of the Levenberg-Marquardt algorithm for non-linear curve fitting, to the median stacked spectrum from spaxels in the datacube which contain no object flux and then subtracted from each spaxel in turn. \\

\noindent
The central coordinates of each pointing, the number of target galaxies observed, N$_{obs}$, the number of galaxies with [O~{\sc III}]$\lambda$5007 detected as measured by attempting to fit the redshifted line in the integrated galaxy spectrum using the known redshift value, N$_{Det} = 62/77$ $(81\%)$, the number with spatially-resolved [O~{\sc III}]$\lambda$5007 emission, N$_{Res}$ (see \cref{subsubsection:spaxel_fitting}), the on source exposure time and the averaged seeing conditions are listed in Table \ref{tab:pointings}.

@@

\noindent
The difference in position of these relations highlights the main-sequence evolution towards higher SFRs at fixed $M_{\star}$ between $z\simeq2.5-3.5$.
The KDS galaxies scatter, within the errors, consistently above and below the $z\simeq3$ main-sequence.

@@

\subsubsection{Sample summary}\label{subsubsec:sample_summary}
We have observed 77 SFGs spanning $3.0 < z < 3.8$ with the KMOS IFUs as part of the KMOS Deep Survey.
By processing the observations, we have constructed a datacube for each of these galaxies, finding integrated [O~{\sc III}]$\lambda$5007 in 62/77 targets.
We have also derived $M_{\star}$ values and SFRs from SED modelling, finding that these values place the KDS galaxies into regions of parameter space spanned by typical star-forming galaxies at this redshift.
Three KMOS pointings cover the field environment and one pointing covers a cluster environment at the heart of the SSA22 protocluster, and with these data we seek gauge the role of environment in shaping the early evolutionary history of SFGs.
Throughout the following analysis sections we describe the use of high-resolution imaging to make morphological measurements for the KDS galaxies and the extraction of kinematic properties for the galaxies using the [O~{\sc III}]$\lambda$5007 emission line.
Chemical abundance measurements for the KDS galaxies in both the field and cluster environments will be presented in a future work.

@@

\noindent
We first ran SExtractor \citep{Bertin1996} on the relevant images to recover initial input parameters and segmentation maps for running {\scriptsize GALFIT}, and then extracted postage stamp regions around the galaxies in the KDS sample.
At this redshift, the galaxies are more compact and generally we could not resolve more complicated morphological features such as spiral arms and bars and so we followed the simple method of fitting \Sers profiles, with the \Sers index fixed to the exponential disk value of $n=1$.
In the {\it F160W} band, the adopted PSF was a hybrid between the Tiny Tim {\it H}-band model \citep{Krist2011} in the PSF centre and an empirical stack of stars observed in the {\it H}-band for the wings \citep{VanderWel2012} and in the {\it F814W} band we used the pure Tiny Tim {\it ACS} high-resolution PSF model.
During the fitting process all other morphological parameters, including $R_{1/2}$, the central x and y coordinates, $PA_{morph}$ and inclination, were free to vary.

This method was justified by the recovery of similar mean $\chi^{2}$ values when fitting floating \Sers index models and bulge/disk models with both an $n=1$ and $n=4$ component (following the procedure described in \citealt{Bruce2012}) to those recovered from the fixed exponential disk fit.
Additionally, 22 GOODS-S objects were also detected in the \cite{VanderWel2012} catalogue, for which the median \Sers index value is $n=1.2$.
The use of exponential profiles also facilitates comparison with recent large surveys such as KMOS$^{3D}$ \citep{Wisnioski2015} and KROSS \citep{Harrison2017} in which beam-smearing correction factors were applied to the derived kinematic parameters as a function of exponential disk scale length, $R_{D}$, defined as $R_{1/2}\simeq1.68 R_{D}$ (see Appendix \ref{subsec:KROSS}). \\

\noindent
This analysis provided us with three crucial morphological parameters required to support the kinematic analysis of \cref{subsec:3d_modelling}, namely the axis ratio $b/a$, half-light radius $R_{1/2}$ and the morphological position angle $PA_{morph}$.
Example {\em HST} images and {\scriptsize GALFIT} outputs are given in Figure \ref{fig:main_body_kinematic_grids} for selected galaxies, and maps for the full isolated field sample (see \cref{subsubsection:spaxel_fitting}) are plotted throughout Appendix \ref{app:kinematics_plots}.

@@

ID              & RA       & Dec       & z     & K$_{AB}$     & $log(M_{\star}/M_{\odot})^{a}$ & $b/a$ & i$^{\circ}$$^{b}$ & PA$_{morph}^{\circ}$ & R$_{1/2}$(kpc)$^{c}$ \\

@@

b15573          & 03:32:27.638 & $-$27:50:59.676 & 3.583        & 23.6   & 9.8  & 0.28        & 78        & 146   & 0.52      \\

@@

@@

\end{tabular}
\begin{tablenotes}
      \small
      \item $^{a}$ Representative error of 0.2 dex from SED modelling used throughout this study
      \item $^{b}$ Fixed 10 percent inclination error assumed (i.e. $\delta i = i / 10$, see \protect\cref{subsubsection:inclination_angle})
      \item $^{c}$ Fixed 10 percent $R_{1/2}$ error assumed, see \protect\cref{subsubsection:half-light_radii}
      \item $^{*}$ No {\em HST} coverage: $PA_{morph}$ set to $PA_{kin}$ value; $b/a$ and $R_{1/2}$ estimated as explained throughout the text.
    \end{tablenotes}
  \end{threeparttable}
  \end{table*}

@@

\noindent
To derive the inclination, we selected a value for $q_{0}$, and following the discussion in \citep{Law2012a} we chose a value appropriate for thick disks, $q_{0} = 0.2$ \citep[e.g.][]{Epinat2012,Harrison2017}.
However, as discussed in \cite{Harrison2017}, varying the $q_{0}$ value by a factor of 2 makes only a small change to the final inclination corrected velocity values, with the difference $<10\%$ in the case of the KDS galaxies in the isolated field sample (see \cref{subsec:morpho-kin-class}).

@@

%In the right panel of Figure \ref{fig:morpho-distributions} we plot the distribution of the derived $R_{1/2}$ values (for the 28 galaxies with {\em HST} imaging in the refined sample, \cref{subsubsec:kin_sample_summary}) in comparison to the reference samples spanning two redshift ranges.
%In general the KDS galaxies are much more compact than at lower redshift and overlap with the smaller side of the $3 < z < 4$ reference sample, which we attribute to the lack of massive galaxies in the KDS sample (through the mass-size relation \citep[e.g.][]{Trujillo2004}).
\noindent
\cite{Bruce2012} present a detailed error analysis of the morphological parameters of $1 < z < 3$ galaxies in the CANDELS fields (which includes {\em HST} data covering the GOODS-S field which we exploited during this work), reporting that the magnitude of the error on $R_{1/2}$ is typically at the 10$\%$ level.
We adopted a nominal error of 10$\%$ for our recovered $R_{1/2}$ values and note that the errors on $V_{C}$ and $\sigma_{int}$ are dominated by measurement errors and uncertainties connected with assumptions about the inclination angle correction and the velocity dispersion distribution in high-redshift galaxies (see Appendix \ref{app:kin_error_estimates}).

>>>>

% Abstract of the paper
\begin{abstract}
We present dynamical measurements from the KMOS ({\it K}-band Multi-Object Spectrograph) Deep Survey (KDS), which is comprised of 77 typical star-forming galaxies at $z\simeq3.5$ in the mass range $9.0 < log(M_{\star}/M_{\odot}) < 10.5$.
These measurements constrain the internal dynamics, the intrinsic velocity dispersions ($\sigma_{int}$) and rotation velocities ($V_{C}$) of galaxies in the high-redshift Universe.
The mean velocity dispersion of the galaxies in our sample is $\sigma_{int} = 70.8^{+3.3}_{-3.1} km\,s^{-1}$, revealing that the increasing average $\sigma_{int}$ with increasing redshift, reported for $z\lesssim2$, continues out to $z\simeq3.5$.
Only $36 \pm 8\%$ of our galaxies are rotation-dominated ($V_{C}/\sigma_{int}$ > 1), with the sample average $V_{C}/\sigma_{int}$ value much smaller than at lower redshift.
After carefully selecting comparable star-forming samples at multiple epochs, we find that the rotation-dominated fraction evolves with redshift with a $z^{-0.2}$ dependence. 
The rotation-dominated KDS galaxies show no clear offset from the local rotation velocity-stellar mass (i.e. $V_{C}-M_{\star}$) relation, although a smaller fraction of the galaxies are on the relation due to the increase in the dispersion-dominated fraction.
These observations are consistent with a simple equilibrium model picture, in which random motions are boosted in high-redshift galaxies by a combination of the increasing gas fractions, accretion efficiency, specific star-formation rate and stellar feedback and which may provide significant pressure support against gravity on the galactic disk scale.
\end{abstract}

@@

In this paper we present new results from the KMOS Deep Survey (KDS), which is a guaranteed time programme focusing on the spatially-resolved properties of main-sequence SFGs at $z\simeq3.5$, a time when the universe was building to peak activity.
With this survey, we aim to complement existent studies by providing deep IFS data for the largest number of galaxies at this redshift.
By making use of KMOS (with integration times of 7.5-9 hours), we have been able to study [O~{\sc III}]$\lambda$5007 emission in 77 galaxies spanning the mass range $9.0 < log(M_{\star}/M_{\odot}) < 10.5$, roughly \textbf{doubling} the number of galaxies observed via IFS at $z > 3$.
In order to interpret the evolution of the physical properties of typical star-forming galaxies we have carefully constructed a set of comparison samples spanning $0 < z < 3$.
These samples use integral-field spectroscopy to track the ionised gas emission in star-forming galaxies and follow consistent kinematic parameter extraction methods.  
By doing this we seek to minimise the impact of systematic differences introduced by differing approaches to defining and extracting kinematic parameters.

@@

The structure of the paper is as follows.
In \cref{sec:Survey_and_data} we present the survey description, sample selection, observation strategy and data reduction, leading to stacked datacubes for each of the KDS galaxies.
In \cref{sec:analysis} we describe the derivation of morphological and kinematic properties for our galaxies, explaining the kinematic modelling approach and the beam-smearing corrections which lead to intrinsic measurements of the rotation velocities, $V_{C}$, and velocity dispersions $\sigma_{int}$ for each of the galaxies classified as morphologically isolated and spatially-resolved in the [O~{\sc III}]$\lambda$5007 emission line.
\cref{sec:results} presents an analysis of these derived kinematic parameters, comparing with lower redshift work where possible and drawing conclusions about the evolutionary trends and possible underlying physical mechanisms.
We discuss these results in \cref{sec:discussion} and present our conclusions in \cref{sec:conclusion}.
Throughout this work we assume a flat $\Lambda$CDM cosmology with (h, $\Omega_{m}$, $\Omega_{\Lambda}$) = (0.7, 0.3, 0.7).

\section{SURVEY DESCRIPTION, SAMPLE SELECTION AND OBSERVATIONS}\label{sec:Survey_and_data}
\subsection{The KDS survey description and sample selection}\label{subsec:survey_intro}
The KDS is a KMOS study of the gas kinematics and metallicity in 77 SFGs with a median redshift of $z\simeq3.5$, probing a representative section of the galaxy main-sequence.
The addition of these data approximately \textbf{doubles} the number of galaxies observed via IFS at this redshift \textbf{\citep{Cresci2010,Lemoine-Busserolle2010,Gnerucci2011,Troncoso_2014}}, and will allow for a statistically-significant investigation of the dynamics and metal content of SFGs during a crucial period of galaxy evolution. 
The key science goals of the KDS are to investigate the resolved kinematic properties of high-redshift galaxies in the peak epoch of galaxy formation (particularly the fraction of rotating disks and the degree of disk turbulence) and also to study the spatial distribution of metals within these galaxies in the context of their observed dynamics.
We seek to probe both a `field' environment in which the density of galaxies is typical for this redshift and a `cluster' environment containing a known galaxy over-density, in order to gauge the role of environment in determining the kinematics and metallicities of SFGs during this early stage in their formation history.
To achieve this we require very deep exposure times in excess of 7 hours on source to reach the signal-to-noise required to detect line emission in the outskirts of the galaxies where the rotation curves begin to flatten, and to achieve adequate signal-to-noise across several ionised emission lines within individual spatial pixels (spaxels).
Consequently, the KDS is one of the deepest spectroscopic datasets available at this redshift.

@@

 \hline
Pointing & RA & DEC & N$_{obs}$ & N$_{Det}$ & $\%$ Det. & N$_{Res}$ & $\%$ Res & N$_{Merg}$ & $\%$ Merg$^{*}$ & Band$^{a}$ & Exp (ks) & PSF ($^{\prime\prime}$)$^{b}$  \\
 \hline
 \scriptsize{\bf GOODS-S-P1(field)} & 03:32:25.910 & $-$27:51:58.710 & 20 & 17 & 85 & 14 & 70 & 2 & 17 & {\it K} & 32.4 & 0.50 \\
\scriptsize{\bf GOODS-S-P2(field)} & 03:32:32.217 & $-$27:43:08.000 & 17 & 14 & 82 & 13 & 76 & 2 & 18 & {\it K} & 31.8 & 0.52 \\
\scriptsize{\bf SSA22-P1(cluster)} & 22:17:11.867 & $+$00:15:44.700 & 21 & 15 & 71 & 9 & 46 & 8 & 89 & {\it HK} & 38.1 & 0.62 \\
\scriptsize{\bf SSA22-P2(field)} & 22:17:35.120 & $+$00:09:30.500 & 19 & 17 & 89 & 12 & 63 & 2 & 18 & {\it HK} & 27.8 & 0.57 \\

@@

We prepared each pointing using the KARMA tool \citep{Wegner2008}, taking care to allocate at least one IFU to observations of a `control' star closeby on the sky to allow for precise monitoring of the evolution of seeing conditions and the shift of the telescope away from the prescribed dither pattern (see \cref{subsubsec:datareduction}).
For the four pointings described above and summarised in Table \ref{tab:pointings}, we adopted the standard object-sky-object (OSO) nod-to-sky observation pattern, with 300s exposures and alternating $0.2^{\prime\prime}$/$0.1^{\prime\prime}$ dither pattern for increased spatial sampling around each of the target galaxies.
This procedure allowed for datacube reconstruction with 0.1$^{\prime\prime}$ size spaxels as described in \cref{subsubsec:datareduction}. \\

The observations were carried out during ESO observing periods P92-P96 using Guaranteed Time Observations (Programme IDs: 092.A-0399(A), 093.A-0122(A,B), 094.A-0214(A,B),095.A-0680(A,B),096.A-0315(A,B,C)) with excellent seeing conditions.
In GOODS-S-P1 and GOODS-S-P2 the median {\it K}-band seeing was $\simeq0.5^{\prime\prime}$ and for the SSA22-cluster and SSA22-field pointings the {\it K}-band seeing ranged between $\simeq0.55-0.65^{\prime\prime}$.
We observed 17-21 $z\simeq3.5$ targets in each field (see Table \ref{tab:pointings}), with these numbers less than the available 24 arms for each pointing due to the combination of three broken pickoff arms during the P92/93 observing semesters and our requirement to observe at least one control star throughout an Observing Block (OB). \\

This paper is concerned with the spatially-resolved kinematics of the KDS galaxies.
Consequently, we now focus exclusively on the spatially-resolved [O~{\sc III}]$\lambda$5007 measurements in the {\it K}-band spectral window. 
The details of the {\it H}-band data reduction and corresponding metallicity analyses will be described in a future study.

@@

The SPARK recipes were used to create dark frames and to flatfield, illumination correct and wavelength calibrate the raw data.
An additional step, which is not part of the standard reduction process, was carried out at this stage, to address readout channel bias.
Differences in the readout process within each 64-pixel wide channel on the detector image lead to varying flux baselines \textbf{across each of the individual exposures}.
We corrected back to a uniform flux baseline across the detector image for each object exposure by identifying pixels which are not illuminated in every readout channel and subtracting their median value from the rest of the pixels in the channel.
\textbf{This is a separate issue to non-uniform illumination across the detectors, which is corrected by applying the illumination correction frame to the stacked datacubes}.

Standard star observations were carried out on the same night as the science observations and were processed in an identical manner to the science data.
Following this pre-processing, each of the object exposures was reconstructed independently, using the closest sky exposure for subtraction, to give more control over the construction of the final stacks for each target galaxy.
Each 300s exposure was reconstructed into a datacube with interpolated $0.1\times0.1^{\prime\prime}$ spaxel size, facilitated by the subpixel dither pattern discussed in \cref{subsubsec:Obs} which boosts the effective pixel scale of the observations. \\

Sky subtraction was enhanced using the SKYTWEAK option within SPARK \citep{Davies2007}, which counters the varying amplitude of OH lines between exposures by scaling `families' of OH lines independently to match the data.
Wavelength miscalibration between exposures due to spectral flexure of the instrument is also accounted for by applying spectral shifts to the OH families during the procedure, and in general the use of the SKYTWEAK option in the {\it K}-band greatly reduces the sky-line residuals. 
We monitored the evolution of the atmospheric PSF and the position of the control stars over the OBs, to allow us to reject raw frames where the averaged {\it K}-band seeing rose above $0.8^{\prime\prime}$ and to measure the spatial shifts required for the final stack more precisely.
The PSF was determined by fitting the collapsed {\it K}-band image of the stacked control stars in each pointing with an elliptical gaussian, with the values reported in Table \ref{tab:pointings}.
The telescope tends to drift from its acquired position over the course of an OB and the difference between the dither pattern shifts and the measured position of the control stars provides the value by which each exposure must be shifted to create the stack. \\

We stacked all 300s exposures for each galaxy which pass the seeing criteria using 3-sigma clipping, leaving us with a flux and wavelength-calibrated datacube for every object in the KDS sample.
We have found that the thermal background is often under-subtracted across the spatial extent of the cube following a first pass through the pipeline, leading to excess flux towards the long wavelength end of the {\it K}-band.
To account for this, a polynomial function is fit, using the python package {\scriptsize LMFIT} \citep{Newville2014}, which makes use of the Levenberg-Marquardt algorithm for non-linear curve fitting, to the median stacked spectrum from spaxels in the datacube which contain no object flux and then subtracted from each spaxel in turn. \\

The central coordinates of each pointing, the number of target galaxies observed, N$_{obs}$, the number of galaxies with [O~{\sc III}]$\lambda$5007 detected as measured by attempting to fit the redshifted line in the integrated galaxy spectrum using the known redshift value, N$_{Det} = 63/77$ $(82\%)$, the number with spatially-resolved [O~{\sc III}]$\lambda$5007 emission, N$_{Res}$ (see \cref{subsubsection:spaxel_fitting}), the on source exposure time and the averaged seeing conditions are listed in Table \ref{tab:pointings}.

@@

The difference in position of these relations highlights the main-sequence evolution towards higher SFRs at fixed $M_{\star}$ between $z\simeq2.5-3.5$.
The KDS galaxies scatter, within the errors, consistently above and below the $z\simeq3$ main-sequence.

@@

@@

We first ran SExtractor \citep{Bertin1996} on the relevant images to recover initial input parameters and segmentation maps for running {\scriptsize GALFIT}, and then extracted postage stamp regions around the galaxies in the KDS sample.
At this redshift, the galaxies are more compact and generally we could not resolve more complicated morphological features such as spiral arms and bars and so we followed the simple method of fitting \Sers profiles, with the \Sers index fixed to the exponential disk value of $n=1$.
In the {\it F160W} band, the adopted PSF was a hybrid between the Tiny Tim {\it H}-band model \citep{Krist2011} in the PSF centre and an empirical stack of stars observed in the {\it H}-band for the wings \citep{VanderWel2012} and in the {\it F814W} band we used the pure Tiny Tim {\it ACS} high-resolution PSF model.
During the fitting process all other morphological parameters, including $R_{1/2}$, the central x and y coordinates, $PA_{morph}$ and inclination, were free to vary.

This method was justified by the recovery of similar mean $\chi^{2}$ values when fitting floating \Sers index models and bulge/disk models with both an $n=1$ and $n=4$ component (following the procedure described in \citealt{Bruce2012}) to those recovered from the fixed exponential disk fit.
Additionally, \textbf{24} GOODS-S objects were also detected in the \cite{VanderWel2012} catalogue, for which the median \Sers index value is $n=1.2$.
\textbf{Of these 24 galaxies, 2 are found to have $n>2.5$ (lbg\_32 and lbg\_109, see Appendix \ref{app:kinematics_plots}), although both show disk-like kinematics with a monotonic velocity gradient.
The galaxy lbg\_32 can be fit with an $n=1$ \Sers profile with small residuals, however lbg\_109 has a centrally concentrated light distribution which is not well captured by the $n=1$ profile.
This demonstrates that fitting exponential flux distributions is a valid approach for the sample at large.}
The use of exponential profiles also facilitates comparison with recent large surveys such as KMOS$^{3D}$ \citep{Wisnioski2015} and KROSS \citep{Harrison2017} in which beam-smearing correction factors were applied to the derived kinematic parameters as a function of exponential disk scale length, $R_{D}$, defined as $R_{1/2}\simeq1.68 R_{D}$ (see Appendix \ref{subsec:KROSS}). \\

This analysis provided us with three crucial morphological parameters required to support the kinematic analysis of \cref{subsec:3d_modelling}, namely the axis ratio $b/a$, half-light radius $R_{1/2}$ and the morphological position angle $PA_{morph}$.
Example {\em HST} images and {\scriptsize GALFIT} outputs are given in Figure \ref{fig:main_body_kinematic_grids} for selected galaxies, and maps for the full isolated field sample (see \cref{subsubsection:spaxel_fitting}) are plotted throughout Appendix \ref{app:kinematics_plots}.

@@

ID              & RA       & Dec       & z     & K$_{AB}^{a}$     & $log(M_{\star}/M_{\odot})^{b}$ & $b/a$ & i$^{\circ}$$^{c}$ & PA$_{morph}^{\circ}$ & R$_{1/2}$(kpc)$^{d}$ \\

@@

b15573          & 03:32:27.638 & $-$27:50:59.676 & 3.583        & 23.60   & 9.8  & 0.28        & 78        & 146   & 0.52      \\

@@

lbg\_121        & 03:32:19.606 & $-$27:48:40.032 & 3.708      & 25.36  & 9.1    & 0.65        & 50        & 106    & 0.42      \\

@@

\end{tabular}
\begin{tablenotes}
      \small
      \item $^{a}$ \textbf{K-band magnitude errors are typically $\pm0.05$ magnitudes.}
      \item $^{b}$ Representative error of 0.2 dex from SED modelling used throughout this study \textbf{(see \cref{subsubsec:sed_fitting})}.
      \item $^{c}$ Fixed 10 percent inclination error assumed (i.e. $\delta i = i / 10$, see \protect\cref{subsubsection:inclination_angle})
      \item $^{d}$ Fixed 10 percent $R_{1/2}$ error assumed (see \protect\cref{subsubsection:half-light_radii}).
      \item $^{*}$ No {\em HST} coverage: $PA_{morph}$ set to $PA_{kin}$ value; $b/a$ and $R_{1/2}$ estimated as explained throughout the text.
    \end{tablenotes}
  \end{threeparttable}
  \end{table*}

@@

To derive the inclination, we selected a value for $q_{0}$, and following the discussion in \citep{Law2012a} we chose a value appropriate for thick disks, $q_{0} = 0.2$ \citep[e.g.][]{Epinat2012,Harrison2017}.
However, as discussed in \cite{Harrison2017}, varying the $q_{0}$ value by a factor of 2 makes only a small change to the final inclination corrected velocity values, with the difference $<10\%$ in the case of the KDS galaxies in the isolated field sample (see \cref{subsec:morpho-kin-class}).

@@

%In the right panel of Figure \ref{fig:morpho-distributions} we plot the distribution of the derived $R_{1/2}$ values (for the 28 galaxies with {\em HST} imaging in the refined sample, \cref{subsubsec:kin_sample_summary}) in comparison to the reference samples spanning two redshift ranges.
%In general the KDS galaxies are much more compact than at lower redshift and overlap with the smaller side of the $3 < z < 4$ reference sample, which we attribute to the lack of massive galaxies in the KDS sample (through the mass-size relation \citep[e.g.][]{Trujillo2004}).

\cite{Bruce2012} present a detailed error analysis of the morphological parameters of $1 < z < 3$ galaxies in the CANDELS fields (which includes {\em HST} data covering the GOODS-S field which we exploited during this work), reporting that the magnitude of the error on $R_{1/2}$ is typically at the 10$\%$ level.
We adopted a nominal error of 10$\%$ for our recovered $R_{1/2}$ values and note that the errors on $V_{C}$ and $\sigma_{int}$ are dominated by measurement errors and uncertainties connected with assumptions about the inclination angle correction and the velocity dispersion distribution in high-redshift galaxies (see Appendix \ref{app:kin_error_estimates}).

To measure $R_{1/2}$ for the 4 galaxies without {\em HST} coverage, we fit the [O~{\sc III}]$\lambda$5007 narrow-band images with an exponential profile, and subtracted the appropriate PSF from the recovered $R_{1/2}$ value.
We note that the extracted rotation velocities are not sensitive to the precise $R_{1/2}$ values, since we measure these at $2R_{1/2}$ (see \cref{subsubsec:beam_smearing_corrected_velocities}) where the intrinsic model rotation curves have already reached flattening.
